Paper figures

### 2019-01-18 paper_figures.Rmd
edits

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, paged.print=FALSE, echo=FALSE, dev=c('svg', 'png'))
knitr::opts_chunk$set(fig.width=8, fig.height=6) 
library(phyloseq)
library(magrittr)
library(tidyverse)
library(reshape2)
library(ggsignif)
library(DESeq2)

@@

```{r}
filt_alpha <- alpha_div %>% 
  filter(timepoint %in% c('T1', 'T2', 'T3')) %>%
  select('Description','condizione','timepoint','Observed', 'se.chao1', 'Simpson', 'Shannon') %>%
  rename('se.chao1' = 'Chao1') %>%
  mutate(t=as.numeric(stringr::str_sub(timepoint,2,2))) %>% droplevels()

@@

```{r}
knitr::kable(ttest_res)
```

```{r fig3a, fig.cap='Fig 3A: Alpha diversity controls T1 vs T2 and pre and post challenge T2 vs T3', fig.height=5, fig.width=5}
annot_df <- (ttest_res %>% filter(Measure == 'Chao1') %>% filter(pvalue < 0.05) %>% mutate(pvalue = paste('p=',signif(pvalue,2), sep = '')))
filt_alpha %>%
  melt(id.vars = c('Description','condizione','timepoint'), measure.vars =  c('Chao1')) %>%
  ggplot(aes(timepoint, value)) +
  geom_boxplot(aes(fill=timepoint), width=0.8, alpha=.8) +
  xlab('Timepoint') +
  ylab('Chao1 Index') +
  scale_fill_manual(name = "Timepoint", values = cm_palette) +
  # ggsignif::geom_signif(comparisons = list(c('T1','T3')), y_position = 240, tip_length = 0, test = 't.test') +
  # ggsignif::geom_signif(comparisons = list(c('T2','T3')), y_position = 230, tip_length = 0, test = 't.test') +
  geom_signif(data = annot_df, manual=TRUE, aes(annotations = pvalue, xmin=Timepoint1, xmax=Timepoint2, y_position = c(235,225))) +
  guides(fill=FALSE) +
  theme_cm()
```

@@

```{r Plot ordination, fig.cap="Fig 3B: Beta diversity differences pre and post challange T2 vs T3", fig.dim = c(6,5)}
subset(ordwu, timepoint %in% c('T2','T3')) %>%
ggplot(aes(Axis.1, Axis.2)) +
  geom_point(aes(color=timepoint), size=3, alpha=.8) +
  scale_color_manual(name = "Timepoint", values = cm_palette[c(2,3)]) +
  theme_cm() +
  annotation_custom(grob = grid::textGrob(label = bquote(atop("p-value"==.(permanova$aov.tab$`Pr(>F)`[1]),italic(R^2)==.(signif(permanova$aov.tab$R2[1], 2)))),
    gp=grid::gpar(col="black", fontsize=11)),  xmin = 0.15, xmax = .15, ymin = .12, ymax = .12)
```

@@

```{r DESeq2 T2 T3}
res_genus <- DESeq2::results(dds_genus, contrast = c('timepoint', 'T2','T3'), alpha = 0.05)
res.filt_genus <- res_genus[!is.na(res_genus$padj),]
res.filt_genus <- res.filt_genus[res.filt_genus$padj<0.05,]

@@

```{r}
lacno_bact_relabs <- genus_ab_t %>% 
                     bind_cols(data.frame(tax_table(gg_topi.genus.relab)[genus_ab_t$OTU,c('Phylum','Family','Genus')])) %>% 
                     filter(Family %in% c('Bacteroidales S24-7 group') | Genus %in% c('Lachnospiraceae NK4A136 group')) %>% 
                     mutate(taxlab = str_replace(ifelse(stringr::str_detect(Genus,'uncultured'), paste(Family,sep = ''), paste(Genus, sep = '')), ' group','')) %>%
                     select(taxlab, Abundance, timepoint, OTU)

@@

```{r fig.cap="Fig 3C: Differential abundance analysis highlighted Bacteroidales S24/7 and Lacnospiraceae as most differential abunant families.", fig.dim=c(6,5)}
annot_data <- res.filt_genus[unique(lacno_bact_relabs$OTU),] %>% 
              data.frame %>% 
              rownames_to_column('OTU') %>% 
              bind_cols(taxlab = c('Lachnospiraceae NK4A136','Bacteroidales S24-7'),  xmin = c('T2','T2'), timepoint = c('T3','T3'), y_position =  c(0.6,0.7)) %>%
              select(annotations = padj, taxlab, timepoint, xmin, y_position)

@@

```{r fig.cap="Fig 3D: Ordination centroids beta diversity all timepoints", fig.dim = c(6,5)}
not12 <- gg_topi %>%
  subset_samples(!(timepoint %in% c("T1", "T2")))

@@

## Panel ?: Ordination beta diversity T3 vs T7
```{r, fig.dim = c(6, 5)}
metadata_2cat <- mappingfile[mappingfile$timepoint %in% c('T7','T3'),]
distwu_2cat <- phyloseq::distance(subset_samples(gg_topi, timepoint %in% c('T7','T3')), "wunifrac")
permanova <- vegan::adonis(formula = distwu_2cat ~ merge_timepoint, data = metadata_2cat)

@@

mmtx <- model.matrix(object = ~timepoint + timepoint:real_vaccine + timepoint:real_bifido + timepoint:real_vaccine:real_bifido, data = data.frame(ggtopi_subs@sam_data))
idx <- which(apply(mmtx, 2, function(x) all(x==0)))
mmtx <- mmtx[,-idx]

@@

```{r}
res37 <- DESeq2::results(dds_genus, name = "timepointT7", alpha = 0.05)
res37.filt <- res37[!is.na(res37$padj),]
res37.filt <- res37.filt[res37.filt$padj<0.05,]

@@

```{r fig3E, fig.cap="Fig 3E: Boxplot of abundance of significant genera from DESeq2 differential analysis. Genera with median below 1% are filtered", fig.height=6}
genus_ab_t %>%
  bind_cols(data.frame(tax_table(ggtopi_subs.genus.relab)[genus_ab_t$OTU,c('Phylum','Family','Genus')])) %>%
  filter(OTU %in% (genus_ab_t %>%
  group_by(OTU, timepoint) %>%
  summarise(median=median(Abundance)) %>%
  group_by(OTU) %>%
  summarise(filt=min(median)>0.01) %>% filter(filt==TRUE))$OTU) %>%
  filter(Phylum != "Unassigned") %>%
  mutate(taxlab = ifelse(stringr::str_detect(Genus,'uncultured'), paste('Uncultured',Family,sep = ' '), paste(Genus))) %>%
ggplot() +
  geom_boxplot(aes(reorder(taxlab, Abundance, FUN = median), Abundance, fill=timepoint),  position = position_dodge(-.85),alpha=.8) +
  facet_grid(Phylum ~ ., scales = "free", space = "free_y", as.table= T) +
  scale_fill_manual(name = "Timepoint", values = cm_palette[c(3,7)]) +
  coord_flip() +
  xlab('') +
  ylab("Relative abundance") +
  theme_cm()
```

```{r supplfig3E, fig.cap="Fig 3E: Boxplot of abundance of significant genera from DESeq2 differential analysis", fig.height=9}
genus_ab_t %>%
  bind_cols(data.frame(tax_table(ggtopi_subs.genus.relab)[genus_ab_t$OTU,c('Phylum','Family','Genus')])) %>%
  filter(Phylum != "Unassigned") %>%
  mutate(taxlab = ifelse(stringr::str_detect(Genus,'uncultured'), paste('Uncultured',Family,sep = ' '), paste(Genus))) %>%
ggplot() +
  geom_boxplot(aes(reorder(taxlab, Abundance, FUN = median), Abundance, fill=timepoint),  position = position_dodge(-.85),alpha=.8) +
  facet_grid(Phylum ~ ., scales = "free", space = "free_y", as.table= T) +
  scale_fill_manual(name = "Timepoint", values = cm_palette[c(3,7)]) +
  coord_flip() +
  scale_y_log10() +
  xlab('') +
  ylab("Relative abundance") +
  theme_cm() +
  theme(strip.text.y = element_text(angle = 360),
        legend.position = "bottom")
```

```{r}
idx_247 <- which(tax_table(gg_topi.genus.relab)[,'Family'] == "Bacteroidales S24-7 group" & tax_table(gg_topi.genus.relab)[,'Genus'] == "uncultured bacterium")
idx_lachno <- which(tax_table(gg_topi.genus.relab)[,'Genus'] == "Lachnospiraceae NK4A136 group" )

@@

```{r fig3F, fig.cap="Fig 3 F: Abundance of Bacteroidales 24/7 and Lachnospiraceae NK4A136 through timepoints and treatment"}
idx_247 <- which(tax_table(gg_topi.genus.relab)[,'Family'] == "Bacteroidales S24-7 group" & tax_table(gg_topi.genus.relab)[,'Genus'] == "uncultured bacterium")
idx_lachno <- which(tax_table(gg_topi.genus.relab)[,'Genus'] == "Lachnospiraceae NK4A136 group" )

@@

```{r}
brayc_ds <- distancesbc %>% 
  dplyr::filter(topo1==topo2) %>%
  dplyr::filter(timepoint1==3) %>%
  dplyr::filter(timepoint2>4) %>%
  dplyr::select(cols, timepoint2, value) %>%
  dplyr::left_join(mappingfile, by=c('cols' = 'Description'))

@@

```{r fig3G, corr tumor braycurtis, fig.cap="Fig 3 G: Scatterplot of tumor size and difference of beta diversity ", fig.height=3}
distancesbc %>% 
  dplyr::filter(topo1==topo2) %>%
  dplyr::filter(timepoint1==3) %>%
  dplyr::filter(timepoint2>4) %>%
  dplyr::select(cols, timepoint2, value) %>%
  dplyr::left_join(mappingfile, by=c('cols' = 'Description')) %>%
  mutate(timepoint = paste('T',timepoint2,'-T3',sep = '')) %>%
  ggplot(aes(value,tumor_mass)) +
  geom_point() +
  facet_wrap(facets = 'timepoint', nrow = 1, shrink = TRUE, scales = 'free_y') +
  geom_line(stat='smooth', method = 'lm', color='red', alpha=0.7, size=.7) + 
  ylab(bquote('Tumor mass'~( mm^3))) +
  xlab('Bray Curtis distance') +
  theme_cm() +
  geom_text(data = ds_corr_braycf, aes(x=x,y=y, label=label), inherit.aes = FALSE)
```

```{r corr tumor braycurtis, fig.cap="Fig 3I: Scatterplot of tumor size and difference of beta diversity ", fig.height=3}
tbl_data <- otu_table(gg_topi.genus.relab)[idx_247,] %>%
  data.frame %>%
  tidyr::gather_("SampleID", "Abundance", colnames(.)) %>%
  mutate(mouseid=stringr::str_sub(.$SampleID,8, 10)) %>%
  mutate(timepoint=stringr::str_sub(.$SampleID,12, 13)) %>%
  mutate(condition= stringr::str_sub(.$SampleID,4, 6)) %>%
  filter(timepoint %in% c('T3','T7')) %>%
  select(-SampleID) %>%
  spread(timepoint,Abundance) %>%
  mutate(diff_abb = T3-T7) %>%
  arrange(mouseid) %>%
  bind_cols( gg_topi.genus.relab %>%
              sample_data %>%
              filter(timepoint == 'T7') %>%
              select(id.topo, tumor_mass) %>%
              arrange(id.topo) %>%
              select(-id.topo))

@@

```{r}
tbl_data %>%
  select(-T3,-T7, -mouseid) %>%
  group_by(condition) %>%
  summarise(diff_abb = list(diff_abb), tumor_mass = list(tumor_mass)) %>%
  group_by(condition) %>%
  mutate(cor.test = paste(unlist(cor.test(unlist(diff_abb), unlist(tumor_mass))[c('p.value','estimate')]), collapse = ' ')) %>%
  separate(cor.test, into = c('p.value','estimate'), sep = ' ')
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  paged.print=FALSE, 
  echo=FALSE, 
  fig.path = 'plots/',
  dev=c('svg', 'png'))
knitr::opts_chunk$set(fig.width=8, fig.height=6) 
library(phyloseq)
library(magrittr)
library(tidyverse)
library(reshape2)
library(ggsignif)
library(DESeq2)

@@

```{r, cache=TRUE}
filt_alpha <- alpha_div %>% 
  filter(timepoint %in% c('T1', 'T2', 'T3')) %>%
  select('Description','condizione','timepoint','Observed', 'se.chao1', 'Simpson', 'Shannon') %>%
  rename('se.chao1' = 'Chao1') %>%
  mutate(t=as.numeric(stringr::str_sub(timepoint,2,2))) %>% droplevels()

@@

```{r, cache=TRUE}
knitr::kable(ttest_res)
```

```{r fig3a, fig.cap='Fig 3A: Alpha diversity controls T1 vs T2 and pre and post challenge T2 vs T3', fig.height=3, fig.width=3}
annot_df <- (ttest_res %>% filter(Measure == 'Chao1') %>% filter(pvalue < 0.05) %>% mutate(pvalue = paste('p=',signif(pvalue,2), sep = '')))
filt_alpha %>%
  melt(id.vars = c('Description','condizione','timepoint'), measure.vars =  c('Chao1')) %>%
  ggplot(aes(timepoint, value)) +
  geom_boxplot(aes(fill=timepoint), width=0.8, alpha=.8) +
  xlab('Timepoint') +
  ylab('Chao1 Index') +
  scale_fill_manual(name = "Timepoint", values = cm_palette) +
  # ggsignif::geom_signif(comparisons = list(c('T1','T3')), y_position = 240, tip_length = 0, test = 't.test') +
  # ggsignif::geom_signif(comparisons = list(c('T2','T3')), y_position = 230, tip_length = 0, test = 't.test') +
  geom_signif(data = annot_df, manual=TRUE, aes(annotations = pvalue, xmin=Timepoint1, xmax=Timepoint2, y_position = c(235,225))) +
  guides(fill=FALSE) +
  theme_cm()
```

@@

```{r fig3b, fig.cap="Fig 3B: Beta diversity differences pre and post challange T2 vs T3", fig.dim = c(6,5)}
subset(ordwu, timepoint %in% c('T2','T3')) %>%
ggplot(aes(Axis.1, Axis.2)) +
  geom_point(aes(color=timepoint), size=3, alpha=.8) +
  scale_color_manual(name = "Timepoint", values = cm_palette[c(2,3)]) +
  theme_cm() +
  annotation_custom(grob = grid::textGrob(label = bquote(atop("p-value"==.(permanova$aov.tab$`Pr(>F)`[1]),italic(R^2)==.(signif(permanova$aov.tab$R2[1], 2)))),
    gp=grid::gpar(col="black", fontsize=11)),  xmin = 0.15, xmax = .15, ymin = .12, ymax = .12)
```

@@

```{r DESeq2 T2 T3, cache=TRUE}
res_genus <- DESeq2::results(dds_genus, contrast = c('timepoint', 'T2','T3'), alpha = 0.05)
res.filt_genus <- res_genus[!is.na(res_genus$padj),]
res.filt_genus <- res.filt_genus[res.filt_genus$padj<0.05,]

@@

```{r, cache=TRUE}
lacno_bact_relabs <- genus_ab_t %>% 
                     bind_cols(data.frame(tax_table(gg_topi.genus.relab)[genus_ab_t$OTU,c('Phylum','Family','Genus')])) %>% 
                     filter(Family %in% c('Bacteroidales S24-7 group') | Genus %in% c('Lachnospiraceae NK4A136 group')) %>% 
                     mutate(taxlab = str_replace(ifelse(stringr::str_detect(Genus,'uncultured'), paste(Family,sep = ''), paste(Genus, sep = '')), ' group','')) %>%
                     select(taxlab, Abundance, timepoint, OTU)

@@

```{r fig3c, fig.cap="Fig 3C: Differential abundance analysis highlighted Bacteroidales S24/7 and Lacnospiraceae as most differential abunant families.", fig.dim=c(6,5)}
annot_data <- res.filt_genus[unique(lacno_bact_relabs$OTU),] %>% 
              data.frame %>% 
              rownames_to_column('OTU') %>% 
              bind_cols(taxlab = c('Lachnospiraceae NK4A136','Bacteroidales S24-7'),  xmin = c('T2','T2'), timepoint = c('T3','T3'), y_position =  c(0.6,0.7)) %>%
              select(annotations = padj, taxlab, timepoint, xmin, y_position)

@@

```{r fig3d, fig.cap="Fig 3D: Ordination centroids beta diversity all timepoints", fig.dim = c(6,5)}
not12 <- gg_topi %>%
  subset_samples(!(timepoint %in% c("T1", "T2")))

@@

## Panel ?: Ordination beta diversity T3 vs T7
```{r fig3x, fig.dim = c(6, 5)}
metadata_2cat <- mappingfile[mappingfile$timepoint %in% c('T7','T3'),]
distwu_2cat <- phyloseq::distance(subset_samples(gg_topi, timepoint %in% c('T7','T3')), "wunifrac")
permanova <- vegan::adonis(formula = distwu_2cat ~ merge_timepoint, data = metadata_2cat)

@@

mmtx <- model.matrix(object = ~ timepoint + timepoint:real_vaccine + timepoint:real_bifido + timepoint:real_vaccine:real_bifido, data = data.frame(ggtopi_subs@sam_data))
idx <- which(apply(mmtx, 2, function(x) all(x==0)))
mmtx <- mmtx[,-idx]

@@

```{r, cache=TRUE}
res37 <- DESeq2::results(dds_genus, name = "timepointT7", alpha = 0.05)
res37.filt <- res37[!is.na(res37$padj),]
res37.filt <- res37.filt[res37.filt$padj<0.05,]

@@

```{r fig3e, fig.cap="Fig 3E: Boxplot of abundance of significant genera from DESeq2 differential analysis. Genera with median below 1% are filtered", fig.height=6}
genus_ab_t %>%
  bind_cols(data.frame(tax_table(ggtopi_subs.genus.relab)[genus_ab_t$OTU,c('Phylum','Family','Genus')])) %>%
  filter(OTU %in% (genus_ab_t %>%
  group_by(OTU, timepoint) %>%
  summarise(median=median(Abundance)) %>%
  group_by(OTU) %>%
  summarise(filt=min(median)>0.01) %>% filter(filt==TRUE))$OTU) %>%
  filter(Phylum != "Unassigned") %>%
  mutate(taxlab = ifelse(stringr::str_detect(Genus,'uncultured'), paste('Uncultured',Family,sep = ' '), paste(Genus))) %>%
  mutate(taxlab = ifelse(stringr::str_detect(taxlab,'Unknown'), paste('Unknown',Family,sep = ' '), paste(taxlab))) %>%
  mutate(taxlab = ifelse(stringr::str_detect(taxlab,'Unknown Unknown'), paste('Unknown',Phylum,sep = ' '), paste(taxlab))) %>%
  mutate(taxlab = ifelse(stringr::str_detect(taxlab,'Uncultured uncultured'), paste('Uncultured',Phylum,sep = ' '), paste(taxlab))) %>%
ggplot() +
  geom_boxplot(aes(reorder(taxlab, Abundance, FUN = median), Abundance, fill=timepoint),  position = position_dodge(-.85),alpha=.8) +
  facet_grid(Phylum ~ ., scales = "free", space = "free_y", as.table= T) +
  scale_fill_manual(name = "Timepoint", values = cm_palette[c(3,7)]) +
  coord_flip() +
  xlab('') +
  ylab("Relative abundance") +
  theme_cm()
```

```{r supplfig3e, fig.cap="Fig 3E: Boxplot of abundance of significant genera from DESeq2 differential analysis", fig.height=9}
genus_ab_t %>%
  bind_cols(data.frame(tax_table(ggtopi_subs.genus.relab)[genus_ab_t$OTU,c('Phylum','Family','Genus')])) %>%
  filter(Phylum != "Unassigned") %>%
  mutate(taxlab = ifelse(stringr::str_detect(Genus,'uncultured'), paste('Uncultured',Family,sep = ' '), paste(Genus))) %>%
  mutate(taxlab = ifelse(stringr::str_detect(taxlab,'Unknown'), paste('Unknown',Family,sep = ' '), paste(taxlab))) %>%
  mutate(taxlab = ifelse(stringr::str_detect(taxlab,'Unknown Unknown'), paste('Unknown',Phylum,sep = ' '), paste(taxlab))) %>%
  mutate(taxlab = ifelse(stringr::str_detect(taxlab,'Uncultured uncultured'), paste('Uncultured',Phylum,sep = ' '), paste(taxlab))) %>%
ggplot() +
  geom_boxplot(aes(reorder(taxlab, Abundance, FUN = median), Abundance, fill=timepoint),  position = position_dodge(-.85),alpha=.8) +
  facet_grid(Phylum ~ ., scales = "free", space = "free_y", as.table= T) +
  scale_fill_manual(name = "Timepoint", values = cm_palette[c(3,7)]) +
  coord_flip() +
  scale_y_log10() +
  xlab('') +
  ylab("Relative abundance") +
  theme_cm() +
  theme(strip.text.y = element_text(angle = 360),
        legend.position = "bottom")
```

```{r, cache=TRUE}
idx_247 <- which(tax_table(gg_topi.genus.relab)[,'Family'] == "Bacteroidales S24-7 group" & tax_table(gg_topi.genus.relab)[,'Genus'] == "uncultured bacterium")
idx_lachno <- which(tax_table(gg_topi.genus.relab)[,'Genus'] == "Lachnospiraceae NK4A136 group" )

@@

```{r fig3f, fig.cap="Fig 3 F: Abundance of Bacteroidales 24/7 and Lachnospiraceae NK4A136 through timepoints and treatment"}
idx_247 <- which(tax_table(gg_topi.genus.relab)[,'Family'] == "Bacteroidales S24-7 group" & tax_table(gg_topi.genus.relab)[,'Genus'] == "uncultured bacterium")
idx_lachno <- which(tax_table(gg_topi.genus.relab)[,'Genus'] == "Lachnospiraceae NK4A136 group" )

@@

```{r, cache=TRUE}
brayc_ds <- distancesbc %>% 
  dplyr::filter(topo1==topo2) %>%
  dplyr::filter(timepoint1==3) %>%
  dplyr::filter(timepoint2>4) %>%
  dplyr::select(cols, timepoint2, value) %>%
  dplyr::left_join(mappingfile, by=c('cols' = 'Description'))

@@

```{r fig3g, include=FALSE, eval=FALSE, fig.height=3,fig.cap="Fig 3 G: Scatterplot of tumor size and difference of beta diversity "}
distancesbc %>% 
  dplyr::filter(topo1==topo2) %>%
  dplyr::filter(timepoint1==3) %>%
  dplyr::filter(timepoint2>4) %>%
  dplyr::select(cols, timepoint2, value) %>%
  dplyr::left_join(mappingfile, by=c('cols' = 'Description')) %>%
  mutate(timepoint = paste('T',timepoint2,'-T3',sep = '')) %>%
  ggplot(aes(value,tumor_mass)) +
  geom_point() +
  facet_wrap(facets = 'timepoint', nrow = 1, shrink = TRUE, scales = 'free_y') +
  geom_line(stat='smooth', method = 'lm', color='red', alpha=0.7, size=.7) + 
  ylab(bquote('Tumor mass'~( mm^3))) +
  xlab('Bray Curtis distance') +
  theme_cm() +
  geom_text(data = ds_corr_braycf, aes(x=x,y=y, label=label))
```

```{r fig3i, fig.cap="Fig 3I: Scatterplot of tumor size and difference of beta diversity ", fig.height=3}
tbl_data <- otu_table(gg_topi.genus.relab)[idx_247,] %>%
  data.frame %>%
  tidyr::gather_("SampleID", "Abundance", colnames(.)) %>%
  mutate(mouseid=stringr::str_sub(.$SampleID,8, 10)) %>%
  mutate(timepoint=stringr::str_sub(.$SampleID,12, 13)) %>%
  mutate(condition= stringr::str_sub(.$SampleID,4, 6)) %>%
  filter(timepoint %in% c('T3','T7')) %>%
  select(-SampleID) %>%
  spread(timepoint,Abundance) %>%
  mutate(diff_abb = T3-T7) %>%
  arrange(mouseid) %>%
  bind_cols( gg_topi.genus.relab %>%
              sample_data %>%
              filter(timepoint == 'T7') %>%
              select(id.topo, tumor_mass) %>%
              arrange(id.topo) %>%
              select(-id.topo))

@@

```{r, cache=TRUE}
tbl_data %>%
  select(-T3,-T7, -mouseid) %>%
  group_by(condition) %>%
  summarise(diff_abb = list(diff_abb), tumor_mass = list(tumor_mass)) %>%
  group_by(condition) %>%
  mutate(cor.test = paste(unlist(cor.test(unlist(diff_abb), unlist(tumor_mass))[c('p.value','estimate')]), collapse = ' ')) %>%
  separate(cor.test, into = c('p.value','estimate'), sep = ' ')
```
